Comparing Different Planned Missingness Designs in Longitudinal Studies

### 2018-06-09 Documentation/response.Rnw

 We should also note that this revision is a little bit unusual in that the main author of the first submission has been dropped from this manuscript.  Since then two other authors have been added to this manuscript, which has had parts largely re-written and the simulation study has been completely overhauled to conform to standards of reproducible research.

\section{Referee 1}
\subsection{Comments to the Author}
\begin{itemize}

\item {[Issues]} that are specific to longitudinal studies (e.g., drop-out) should be discussed in light of the advantages of planned missing designs.\\

{\bf This first iteration of this paper did not provide adequate context. This particular concern is addressed in the addition of an introductory paragraph.}\\

{\bf With any high frequency longitudinal study, there is a high probability of dropout.  Using planned missingness reduces the burden on the participants, which often lowers the probability of drop out due to survey fatigue.  It can also lower the cost of a longitudinal study.  We believe this is addressed in the second sentence of the first paragraph of the new draft of the manuscript.}\\

@@

\item  The level of detail is more than readers need to get the essentials and pointing out that researchers have to choose how many blocks to include in any design is extraneous information and distracts from the larger argument.\\

{\bf We believe that we have addressed this issue by re-writing and cleaning up large sections of the manuscript, which we believe now contain the appropriate level of detail.  }\\
%We have re-written this whole section and we believe it now has the appropriate level of detail.

\item Similarly, there is little mention about the mechanics behind multiple imputation - this is an important aspect of the study that deserves more attention than what is included. As a case in point, the authors mention that the choice of imputations is important but never mention why (e.g., improved efficiency). They also fail to mention the importance of the imputation model.\\

{\bf Complete case analysis is highly inefficient here because we would be removing nearly all of the observations.  Multiple imputation gets around this and allows for more efficient estiamtion of the parameters.}\\

@@

{\bf Certainly any simulation study suffers from the flaw that it is difficult to determined how generalizable the results are beyond the specific settings of the particular simulation study.  However, the study design in Pellowski et. al. (2016) is a common design and the planned missingness designs studied here are also common desgined.  \\

That being said, we believe that results would be similar if the response was continuous and / or different parameters were chosen for the covariates.  The sample size of this study is relatively small, but we still see reasonable results.  In Pellowski et. al. (2016) the number of participants was 59.  Sample sizes can be this low when attempting to collect data longitudinally at high frequencies such as daily (or even more often) due to the fact the participants need to be highly engaged in the study.\\

There should have been two omitted responses for Day 5 in the Split Form example in Table 4.  This correction has been made.\\  
}\\

How to respond to this: ``Are these sample sizes typical? And is there good reason to believe that a different design would have produced the same results? For example, is it reasonable to assume that there are no context or order effects in these questions that might play out in at least the split form designs?"\\

@@

{\bf The true parameter values have been added to this table, which is now Table 5. }\\

\item I was troubled by the seemingly arbitrary thresholds for what were unacceptable criteria. How was "Bias, Percent Bias, or MSE more than 40\% greater than the complete-data value or a CI coverage of less than 90\%" determined?\\

{\bf We have removed the mention of these cut-offs.  However, they are based on suggestions put forth in Collins, L. M., Schafer, J. L., & Kam, C.-M. (2001)}\\

\item In section 4.3, the authors seem to confuse the idea of bias and efficiency.\\

{\bf That is correct.  The mentions of efficiency have been removed from this section.  }\\

@@

\end{itemize}

\section{Referee 2}
\subsection{Comments to the Author}
\begin{itemize}

\item  The authors compare their model with the one investigated by Rhemtulla et al. (2014), writing that "because our model of interest is a mixed effects model, though, we cannot be sure that this result will hold." It might be useful to spell out the differences between the two models, because a latent growth curve model can be specified as a mixed effects model. I believe there are three differences in the models: (1) we included a random slope, whereas yours is fixed; (2) we used a "latent basis" model in which the slope coefficients were estimated, whereas yours are fixed to specify linear change, and (3) you included observed predictors whereas we did not. It may be interesting to consider any differences in the results in light of these model differences, in particular, I would have predicted that a linear slope (and especially a fixed linear slope) is less affected by wave-level missingness than a random basis slope, which would seem to require more information at each time point in order to estimate.\\

{\bf The complete data structure is best fit with mixed effects model and mimic the original data.  We now exgend it to the scenario where we have missing by design.  For the structure of this data, we believe this is the best model.}\\

%We're using different data! That's why we didn't use a latent growth curve model.  It's not a comparison.  It's in addition to.

@@

\item The model equation appears to be missing an error term in Level 1. If it isn't, that implies that data were generated with no prediction error - please clarify!\\

{\bf The model was indeed written incorrectly.  The model is now written as $$
logit (p_{ij}) = \beta_{0j} + \beta_1DrinkYN_i + \beta_2ZAlcTox_i +\beta_3Day
$$
where $\beta_{0j} = \gamma_0 + \alpha_j$ and $\alpha_j \sim N(0,\sigma_\alpha^2)$.}\\

\item I'm quite confused about the relation between the survey questions and the analysis model. Table 5 presents the survey questions, which I presumed to be the basis for the planned missing design, but the analysis model doesn't seem to include any of those items except "did you drink today" as a predictor. How is the split form design relevant to the variables included in the model? What was the missingness pattern of those items? More generally, I'd like to see the full model of the complete data that were generated and the details of all the missingness patterns that were imposed (i.e., which variables were missing data on which days in the 25\%, 50\%, and 75\% missing conditions).\\

{\bf The analysis model contains only one of the survey questions, but the other survey questions are used in the imputation model to impute the missing values of the question used in the analysis model.  An example of the missingness pattern for low levels of missingness for split design can be seen in figure 1 in the left-most image.  }\\

@@

\item In the split form design, is Day 5 / Q5 supposed to be missing? It's otherwise strange that Q5 is answered on 4/5 days and that Day 5 as 4/5 questions, as opposed to all the other days/questions being 3/5.\\

{\bf We have removed this table from the manuscript and replaced with this Figure 1.  Figure 1 shows an example of the missingness patterns for one single participant.  }\\

\item Further, please clarify whether that Table 6 presents the PM designs for a single participant. That is, I think another participant would be missing different questions on different days in the Split Form design, or missing different waves in the Wave Missingness design. Normally these design tables (like Tables 1-4) have a column for participants/forms, but Table 6 does not.\\

{\bf The table that the reviewer is referring to has been removed from the manuscript.  It has been replaced by figure 1 and it is indeed an example of the missingness design for one single individual.    }\\

### 2018-06-09 Documentation/response.tex

 We would like to thank the reviewers for their helpful comments on our manuscript.  We have addressed each of these comments in our revised manuscript, as well as provided a point-by-point response below. Reviewer comments are in regular font and our responses are bold-faced.

 We should also note that this revision is a little bit unusual in that the main author of the first submission has been dropped from this manuscript.  Since then two other authors have been added to this manuscript, which has had parts largely re-written and the simulation study has been completely overhauled to conform to standards of reproducible research.

\section{Referee 1}
\subsection{Comments to the Author}
\begin{itemize}

\item {[Issues]} that are specific to longitudinal studies (e.g., drop-out) should be discussed in light of the advantages of planned missing designs.\\

{\bf This first iteration of this paper did not provide adequate context. This particular concern is addressed in the addition of an introductory paragraph.}\\

{\bf With any high frequency longitudinal study, there is a high probability of dropout.  Using planned missingness reduces the burden on the participants, which often lowers the probability of drop out due to survey fatigue.  It can also lower the cost of a longitudinal study.  We believe this is addressed in the second sentence of the first paragraph of the new draft of the manuscript.}\\

%With a high frequency longitudinal there is is a high probabilty of dropout.  Using planned missingesns reduces the burden on participants.  CITE where we talk about this in the paper.

\item {[There]} is no justification for an inherent interest in a multilevel model. Why is this of greater interest than a latent growth curve or a simple repeated measures model?\\

{\bf We chose to work with a multi-level model in this case because that was the analysis model of interest in Pellowski et. al. (2016).  The data used in the aforementioned paper was used a basis for our simulation study, and so we wanted to continue to use the analysis model that was of interest in the original paper.  The justification for using that model can be found in Pellowski et. al. (2016).  }\\
%In the paper by Pellofski YEAR, that was the origianl model of interest.  We are simply using that model of interest in our simulation, now with the addition of planned missingess.

@@

\item Similarly, there is little mention about the mechanics behind multiple imputation - this is an important aspect of the study that deserves more attention than what is included. As a case in point, the authors mention that the choice of imputations is important but never mention why (e.g., improved efficiency). They also fail to mention the importance of the imputation model.\\

{\bf Complete case analysis is highly inefficient here because we would be removing nearly all of the observations.  Multiple imputation gets around this and allows for more efficient estiamtion of the parameters.}\\

\item {[The]} empirical example is so specific that I am not sure one can generalize beyond the limited set of simulations that were examined here.  For example, can we reasonably assume that these findings would generalize to a continuous outcome? What about different parameters for the covariates? Are these sample sizes typical? And is there good reason to believe that a different design would have produced the same results? For example, is it reasonable to assume that there are no context or order effects in these questions that might play out in at least the split form designs?  Of course, this is a flaw of any simulation; however, the highly specific nature of this study stands out. As an aside, why is there only one omitted response for day 5 (Q3)?\\

{\bf Certainly any simulation study suffers from the flaw that it is difficult to determined how generalizable the results are beyond the specific settings of the particular simulation study.  However, the study design in Pellowski et. al. (2016) is a common design and the planned missingness designs studied here are also common desgined.  \\

That being said, we believe that results would be similar if the response was continuous and / or different parameters were chosen for the covariates.  The sample size of this study is relatively small, but we still see reasonable results.  In Pellowski et. al. (2016) the number of participants was 59.  Sample sizes can be this low when attempting to collect data longitudinally at high frequencies such as daily (or even more often) due to the fact the participants need to be highly engaged in the study.\\

There should have been two omitted responses for Day 5 in the Split Form example in Table 4.  This correction has been made.\\  
}\\

How to respond to this: ``Are these sample sizes typical? And is there good reason to believe that a different design would have produced the same results? For example, is it reasonable to assume that there are no context or order effects in these questions that might play out in at least the split form designs?"\\

@@

\item In table 7 it would be useful to have the true parameter values next to the parameter.\\

{\bf The true parameter values have been added to this table, which is now Table 5. }\\

\item I was troubled by the seemingly arbitrary thresholds for what were unacceptable criteria. How was "Bias, Percent Bias, or MSE more than 40\% greater than the complete-data value or a CI coverage of less than 90\%" determined?\\

{\bf We have removed the mention of these cut-offs.  However, they are based on suggestions put forth in Collins, L. M., Schafer, J. L., & Kam, C.-M. (2001)}\\

@@

\item In section 4.3, the authors seem to confuse the idea of bias and efficiency.\\

{\bf That is correct.  The mentions of efficiency have been removed from this section.  }\\

@@

\end{itemize}

\section{Referee 2}
\subsection{Comments to the Author}
\begin{itemize}

\item  The authors compare their model with the one investigated by Rhemtulla et al. (2014), writing that "because our model of interest is a mixed effects model, though, we cannot be sure that this result will hold." It might be useful to spell out the differences between the two models, because a latent growth curve model can be specified as a mixed effects model. I believe there are three differences in the models: (1) we included a random slope, whereas yours is fixed; (2) we used a "latent basis" model in which the slope coefficients were estimated, whereas yours are fixed to specify linear change, and (3) you included observed predictors whereas we did not. It may be interesting to consider any differences in the results in light of these model differences, in particular, I would have predicted that a linear slope (and especially a fixed linear slope) is less affected by wave-level missingness than a random basis slope, which would seem to require more information at each time point in order to estimate.\\

{\bf The complete data structure is best fit with mixed effects model and mimic the original data.  We now exgend it to the scenario where we have missing by design.  For the structure of this data, we believe this is the best model.}\\

%We're using different data! That's why we didn't use a latent growth curve model.  It's not a comparison.  It's in addition to.

\item The model equation appears to be missing an error term in Level 1. If it isn't, that implies that data were generated with no prediction error - please clarify!\\

{\bf The model was indeed written incorrectly.  The model is now written as $$
logit (p_{ij}) = \beta_{0j} + \beta_1DrinkYN_i + \beta_2ZAlcTox_i +\beta_3Day
$$
where $\beta_{0j} = \gamma_0 + \alpha_j$ and $\alpha_j \sim N(0,\sigma_\alpha^2)$.}\\

### 2018-06-09 Documentation/manuscript.Rnw
Manuscript and response edits.

prelim <- kable(df, escape = FALSE, format ="latex", caption = "\\label{tab:prelim} Primary Results (N = 60)") %>%
  collapse_rows(columns = 1:2, latex_hline = "major") %>%
  kable_styling(latex_options = c("scale_down","hold_position"))
@

@@

@@

<<formillustration, fig.cap = "Low missingness", echo = FALSE, message = FALSE, warning = FALSE, fig.keep = TRUE, fig.pos = "H">>=
require(gridExtra)
grid.arrange(splitplot, alternatesplitplot, waveplot, ncol=3)
@

@@

Based on the observed data, the true values of the parameters, $\gamma_0$, $\beta_1$, $\beta_2$, $\beta_3$, and $\sigma_\alpha^2$ were found to be -2.29, 0.28, 0.64, 0.01, and 1.12, respectively. \par
Once the samples were drawn, missingness was added under three different structures. These were the Split-Form and Wave Missingness designs previously mentioned as well as a variation on the Split-Form design where a few measurement occasions (here, two days per participant) are fully observed. To clarify this difference, see the hypothetical application of these designs to a five question multi-day survey in Table \ref{tab:table14} \textbf{Greg: I think we need either only the table or only the illustration.  Not sure we need both.}. As in the previous tables, "1" indicates an observed occasion while "0" indicates a missing one. We see that the Split Form design entails missing two items on each of the days. The altered Split Form, while similar, is fully measured on two of the measurement occasions. Because there are days which are fully observed, the relationships between variables may be clearer, allowing the imputation procedure to run more effectively. On the other hand, the Wave Missingness design shows two days in which no questions are asked but the full questionnaire is given on the remaining days. \par

% \begin{table}[H]
% 	\centering
% 	\caption{Different Planned Missingness Designs}
% 	\setlength{\tabcolsep}{0.45cm}
% 	\label{tab:table14}
% 	\hspace*{-1cm}
% 	\begin{tabular}{c|c|ccccc}
% 		\toprule
% 		Design & Day & Q1 & Q2 & Q3 & Q4 & Q5 \\
% 		\midrule
% 		\multirow{5}{*}{Split Form}
% 		& 1 & 1 & 1 & 0 & 0 & 1 \\
% 		& 2 & 0 & 0 & 1 & 1 & 1 \\
% 		& 3 & 0 & 1 & 1 & 0 & 1 \\
% 		& 4 & 1 & 0 & 1 & 1 & 0 \\
% 		& 5 & 0 & 1 & 0 & 1 & 1 \\
% 		\midrule
% 		\midrule
% 		\multirow{5}{*}{Altered Split Form}
% 		& 1 & 1 & 1 & 1 & 1 & 1 \\
% 		& 2 & 1 & 1 & 1 & 1 & 1 \\
% 		& 3 & 0 & 0 & 1 & 1 & 1 \\
% 		& 4 & 1 & 1 & 0 & 1 & 0 \\
% 		& 5 & 0 & 1 & 1 & 0 & 1 \\
% 		\midrule
% 		\midrule
% 		\multirow{5}{*}{Wave Missingness}
% 		& 1 & 1 & 1 & 1 & 1 & 1 \\
% 		& 2 & 0 & 0 & 0 & 0 & 0 \\
% 		& 3 & 1 & 1 & 1 & 1 & 1 \\
% 		& 4 & 1 & 1 & 1 & 1 & 1 \\
% 		& 5 & 0 & 0 & 0 & 0 & 0 \\
% 		\bottomrule
% 	\end{tabular}
% 	\hspace*{-1cm}	
% \end{table}

%FIX THIS: THIS SOUNDS LIKE WE ADDED MORE MISSINGNESS. FIXED
For each different designed missingness pattern we imposed low, medium, and high levels of missingness roughly corresponding to 2, 4, and 6 missing questions. Previous work by \citet{rhemtulla2014planned} found that for low levels of missingness Split Form design outperforms the Wave Missingness design in capturing latent growth curve model parameters. However, because only low-levels of missingness are tested it is unknown whether this relationship holds at moderate or high levels. By including these different levels of missingness the performance at all levels of the missingness spectrum will be measured. \par
Once missingness was created, Multiple Imputation techniques were applied to estimate the relationship between medication adherence and the other variables in our model. Because the missing data mechanism is controled, the data is known to be MCAR. This fact allows for the principled use of MI techniques. Using the R package \texttt{mice} \citep{mice2011imputation} the binary variables (Q1-Q7) were imputed using a logistic model based approach while the count variable (Q8) was imputed using predictive mean matching %\textbf{was it??? i don't think so, it was in the X block originally but double check!Greg: Yes it was}. 
\par
measure of the proportion of information that is lost as a result of missing data

@@

\subsubsection{Increased Sample Size}
In order to evaluate the impact of sample size on estimation, the original sample size of 60 participants was expanded to 120. The rest of the simulation process was carried out as before. As noted earlier, the cost savings gleaned from the PM designs could allow us to enroll more participants. Thus, even if one design performed more optimally than the others, if all designs also perform acceptably well at high samples, researchers can design missingness in whichever method is most convenient. Furthermore, because Wave Missingness allows for greater savings, an increase in sample size is more reasonable for that type of missingness. \par
\subsubsection{Low Inter-Survey Correlation}
For our second simulation scenario we looked to determine the effect of decreased inter-survey correlation on which PM design would perform best. To clarify, consider the fact that answers given on a particular day may be correlated with one another- the two questions on housing insecurity, for example, are likely to be "yes" on the same days. This set of simulations reduced the correlations between survey questions to study the impact lower correlation between survey question answers.  This was done to simulate a scenario where researchers have a questionnaire that they do not expect any of the answers to be obviously related. To investigate this, the correlation betwen the variables was reduced by half.\par

% While this fact was accounted for in the original simulations, it was not in this set of simulations. If the probability of answering "yes" on Question 2, for instance, was a function of the answer to Question 1 and the baseline variables in the original simulations, then in this scenario it is a function of only the baseline variables. This implies that each of the questions are conditionally independent of each other given the baseline variables. 
\subsubsection{High Time Effect}
In the final scenario, the goal was to determine which PM design would lead to the best estimates when time has a disproportionately large effect on our outcome variable. To do this held the values of $\gamma_0$, $\beta_1$, $\beta_2$ the same and increaed the effect of time (i.e. $\beta_3$) by ten times.  The results of this section may prove useful to researchers who believe that the overall passage of time plays a larger role in their outcome than a measurement taken at one specific point. \par

@@

Of note in the complete-data primary analysis is that the coverage of the 95\% CIs is larger than expected for the parameter estimates and the percent bias for the $\beta_1$ estimate is somewhat large. This increased bias is likely due to the difficulties inherent in estimating logistic regression models with rare event data \citep{king2001logistic}. Nevertheless, this must be kept in mind when analyzing the results from the PM designs provided in Table \ref{tab:primary}. %\textbf{In Table \ref{tab:primary} as in Tables \ref{tab:sampsize}, \ref{tab:lowcorr}, and \ref{tab:hightime} bold values indicate ``unacceptable" results.} That is, bias, percent bias, or MSE more than 40\% greater than the complete-data value or a CI coverage of less than 90\%.

@@

First notice the bias of all parameters is lower than in the smaller sample size simulations. Next, the Split Form design performed similarly well as in the first. At low levels of missingness it gave acceptable results for bias, percent bias, and MSE for the $\beta_1$ and for medium levels only the MSE was unacceptable. However, the CI length is relatively far from the complete-data measurement in Table \ref{tab:prelim}. The CI length from the complete-data simulations was 0.460 while at high levels of missingness the CI length reaches 1.088. Furthermore, the percent bias on the $\beta_1$ estimate is not seriously different from that obtained in the small sample scenario. For example, at medium levels of missingness the percent bias on $\beta_1$ is 23.86\% while for the smaller sample it was 23.75\%.
Similarly to the Split Form design, the Altered Split Form Design also provided unacceptable results for the MSE of the $\beta_1$ estimate at medium missingness and unacceptable bias, percent bias, and MSE at high levels.  \par
For the Wave Missingness design we continue to see the issues observed in the small sample simulations. That is, for the $\beta_1$ estimate the measurements at medium and high levels of missingness are unacceptable and a steep drop off in coverage probability occurs for the 95\% CIs. In fact, at medium and high levels of missingness the coverages drop to 85.5\% and 82.0\%. The $\gamma_0$ parameter also continues to be estimated poorly at high levels of missing data under the Wave Missingness design. \par

@@

For the Split Form design it is important to notice that the bias of the $\beta_1$ estimate decreases much more than in the original simulations when moving from low to high missingess. For instance, the bias of $\beta_1$ at low levels of missingness, here, was found to be -0.041 and -0.145 at high levels. Looking at the same increase in the original simulations, note that the bias only changed from -0.071 to -0.107. \par

@@

With the Split Form and Altered Split Form designs we observed coverage rates for $\beta_1$ paramter estimate that are slightly higher than the nominal level of 95\% coverage in the high, medium, and low levels of missingness.  The percentage of bias in these desgined is relatively low in the -30\% to -50\% range across low, medium, and high missingness.  As for Wave Missingness, the percent bias increases from about -40\% for low missingness all the way up to about -92\% for high missingness.  \par

>>>>

prelim <- kable(df, escape = FALSE, format ="latex", caption = "\\label{tab:prelim} Preliminary Results (N = 60)") %>%
  collapse_rows(columns = 1:2, latex_hline = "major") %>%
  kable_styling(latex_options = c("scale_down","hold_position"))
@

@@

<<echo=FALSE>>=
grid_arrange_shared_legend <- function(...) {
    plots <- list(...)
    g <- ggplotGrob(plots[[1]] + theme(legend.position="bottom"))$grobs
    legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
    lheight <- sum(legend$height)
    grid.arrange(
        do.call(arrangeGrob, lapply(plots, function(x)
            x + theme(legend.position="none"))),
        legend,
        ncol = 1,
        heights = unit.c(unit(1, "npc") - lheight, lheight))
}
@

@@

<<formillustration, fig.cap = "Low missingness", echo = FALSE, message = FALSE, warning = FALSE, fig.keep = TRUE, fig.pos = "H">>=
require(gridExtra)
require(grid)
require(ggplot2)

# plots <- list(splitplot, alternatesplitplot, waveplot)
# g <- ggplotGrob(plots[[1]] + theme(legend.position="bottom"))$grobs
# legend <- g[[which(sapply(g, function(x) x$name) == "guide-box")]]
# lheight <- sum(legend$height)
# tmp <- arrangeGrob(splitplot + theme(legend.position = "none"), alternatesplitplot + theme(legend.position = "none"), layout_matrix = matrix(c(1, 3), nrow = 1))
# grid.arrange(legend, tmp, ncol = 2, heights = c(10,1))

grid.arrange(splitplot, alternatesplitplot, waveplot, ncol=3)
@

@@

Based on the observed data, the true values of the parameters, $\gamma_0$, $\beta_1$, $\beta_2$, $\beta_3$, and $\sigma_\alpha^2$ were found to be -2.29, 0.28, 0.64, 0.01, and 1.12, respectively. \par
Once the samples were drawn, missingness was added under three different structures. These were the Split-Form and Wave Missingness designs previously mentioned as well as a variation on the Split-Form design where a few measurement occasions (here, two days per participant) are fully observed. To clarify this difference, see the hypothetical application of these designs to a five question multi-day survey in Figure \ref{fig:formillustration}. \par

For each different designed missingness pattern we imposed low, medium, and high levels of missingness roughly corresponding to 2, 4, and 6 missing questions. Previous work by \citet{rhemtulla2014planned} found that for low levels of missingness Split Form design outperforms the Wave Missingness design in capturing latent growth curve model parameters. However, because only low-levels of missingness are tested it is unknown whether this relationship holds at moderate or high levels. By including these different levels of missingness the performance at all levels of the missingness spectrum will be measured. \par
Once missingness was created, Multiple Imputation techniques were applied to estimate the relationship between medication adherence and the other variables in our model. Because the missing data mechanism is controled, the data is known to be MCAR. This fact allows for the principled use of MI techniques. Using the R package \texttt{mice} \citep{mice2011imputation} the binary variables (Q1-Q7) were imputed using a logistic model based approach while the count variable (Q8) was imputed using predictive mean matching measure of the proportion of information that is lost as a result of missing data. \par

@@

\subsubsection{Increased Sample Size}
In order to evaluate the impact of sample size on estimation, the original sample size of 60 participants was expanded to 120. The rest of the simulation process was carried out as before. As noted earlier, the cost savings gleaned from the PM designs could allow us to enroll more participants. Thus, even if one design performed more optimally than the others, if all designs also perform acceptably well at high samples, researchers can design missingness in whichever method is most convenient. Furthermore, because Wave Missingness allows for greater savings, an increase in sample size is more reasonable for that type of missingness. \par

\subsubsection{Low Inter-Survey Correlation}
For our second simulation scenario we looked to determine the effect of decreased inter-survey correlation on which PM design would perform best. To clarify, consider the fact that answers given on a particular day may be correlated with one another- the two questions on housing insecurity, for example, are likely to be "yes" on the same days. This set of simulations reduced the correlations between survey questions to study the impact lower correlation between survey question answers.  This was done to simulate a scenario where researchers have a questionnaire that they do not expect any of the answers to be obviously related. To investigate this, the correlation betwen the variables was reduced by half.\par

\subsubsection{High Time Effect}
In the final scenario, the goal was to determine which PM design would lead to the best estimates when time has a disproportionately large effect on our outcome variable. To do this held the values of $\gamma_0$, $\beta_1$, $\beta_2$ the same and increaed the effect of time (i.e. $\beta_3$) by ten times.  The results of this section may prove useful to researchers who believe that the overall passage of time plays a larger role in their outcome than a measurement taken at one specific point. \par

@@

Of note in the complete-data primary analysis is that the coverage of the 95\% CIs is larger than expected for the parameter estimates and the percent bias for the $\beta_1$ estimate is somewhat large. This increased bias is likely due to the difficulties inherent in estimating logistic regression models with rare event data \citep{king2001logistic}. Nevertheless, this must be kept in mind when analyzing the results from the PM designs provided in Table \ref{tab:primary}.

@@

First notice the bias of all parameters is lower than in the smaller sample size simulations. Next, the Split Form design performed similarly well as in the first. At low levels of missingness it gave acceptable results for bias, percent bias, and MSE for the $\beta_1$ and for medium levels only the MSE was unacceptable. However, the CI length is relatively far from the complete-data measurement in Table \ref{tab:prelim}. The CI length from the complete-data simulations was 1.384 while at high levels of missingness the CI length reaches 3.281. However, the percent bias on the $\beta_1$ estimate is seriously different from that obtained in the small sample scenario. For example, at medium levels of missingness the percent bias on $\beta_1$ is -25.97\% while for the smaller sample it was -36.19\%.
Similarly to the Split Form design, the Altered Split Form Design also provided unacceptable results for the MSE of the $\beta_1$ estimate at medium missingness and unacceptable bias, percent bias, and MSE at high levels.  \par
For the Wave Missingness design we continue to see the issues observed in the small sample simulations. That is, for the $\beta_1$ estimate the measurements at medium and high levels of missingness are unacceptable and a steep drop off in coverage probability occurs for the 95\% CIs. In fact, at medium and high levels of missingness the coverages remain steady at 99.4\% and 97\%. The $\gamma_0$ parameter also continues to be estimated poorly at high levels of missing data under the Wave Missingness design. \par

@@

For the Split Form design it is important to notice that the bias of the $\beta_1$ estimate decreases much more than in the original simulations when moving from low to high missingess. For instance, the bias of $\beta_1$ at low levels of missingness, here, was found to be -0.067 and -0.148 at high levels. Looking at the same increase in the original simulations, note that the bias only changed from -0.071 to -0.107. \par

@@

With the Split Form and Altered Split Form designs we observed coverage rates for $\beta_1$ paramter estimate that are slightly higher than the nominal level of 95\% coverage in the high, medium, and low levels of missingness.  The percentage of bias in these designs is relatively low in the -30\% to -50\% range across low, medium, and high missingness.  As for Wave Missingness, the percent bias increases from about -40\% for low missingness all the way up to about -92\% for high missingness.  \par
